Specifying and Verifying the Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
Typos and compressed kamil a bit

\begin{abstract}
Stencil computations are a common programming pattern in numerical
  code and typically form the core of graphics and scientific
  computing applications. However, they are often complex and
  unwieldy, involving substantial fine-grained manipulation of array
  indices across multiple arrays and dimensions. This requires careful
  testing, which is almost always done manually and then discarded
  during development. In this paper, we propose an alternate approach:
  a specification language and automated tool for verifying the
  spatial behaviour of stencils. The specification language is based
  on the hypothesis that stencil computations read from arrays with a
  regular, fixed pattern which can be captured abstractly by a simple
  set of combinators in our specification language. These
  specifications can be embedded as annotations in source code,
  against which code can be checked for conformance. For legacy code,
  spatial specifications can be inferred, providing documentation and
  aiding future software maintenance. We evaluate our language against
  a corpus of numerical Fortran code, and show that the vast majority
  of stencil computations indeed have a simple, regular, static shape
  validating the design of our language.  We introduce the
  language, checking and inference procedures, and its evaluation.
\end{abstract}

@@

% Emphasis here is on documentation generation, so it makes little sense to
% compare this aspect of CamFort to ad hoc testing. Apples and oranges.
\item A specification concisely captures the access pattern of a
  stencil and turns it into documentation. The inference procedure
  efficiently produces specifications with no programmer intervention,
  automatically inserting specifications at appropriate places in the
  source code.
%
%\item Specifications are integrated into the code as comments for easy
%  integration with existing tools, as well as documentation systems (\eg{}, we
%  support Doxygen and FORD syntax).
%
\item Our specification format is deliberately abstract, with a small number of
  combinators that \emph{do not involve any indexing expressions}, \eg{}
  \texttt{a(i+1,j-1)}. This contrasts with other specification approaches. If a
  user specifies, say, the Naiver-Stokes stencil above, in a deductive
  verification language such as ACSL, they must write a specification involving
  textually dense array-indexing expressions. Therefore, any low-level mistakes
  that could be made whilst programming complex indexing code could also be
  made when writing its specification. Our specifications are more lightweight
  with the aim of aiding adoption by scientists and preventing indexing errors.
\end{itemize}

Our verification tool does not target the
class of bugs that can be detected automatically (\emph{push-button
  verification}). Instead, stencil computation bugs must be
identified relative to a specification of the intended access pattern.

>>>>

\begin{abstract}
Stencil computations are a common programming pattern in numerical
  code and typically form the core of graphics and scientific
  computing applications. However, they are often complex and
  unwieldy, involving substantial fine-grained manipulation of array
  indices across multiple arrays and dimensions. This requires careful
  testing, which is almost always done manually and then discarded
  during development. In this paper, we propose an alternate approach:
  a specification language and automated tool for verifying the
  spatial behaviour of stencils. The specification language is based
  on the hypothesis that stencil computations read from arrays with a
  regular, fixed pattern which can be captured abstractly by a simple
  set of combinators in our specification language. These
  specifications can be embedded as annotations in source code,
  against which code can be checked for conformance. For legacy code,
  spatial specifications can be inferred, providing documentation and
  aiding future software maintenance. We evaluate our language against
  a corpus of numerical Fortran code, and show that the vast majority
  of stencil computations indeed have a simple, regular, static shape
  validating the design of our language.  We introduce the
  language, checking, and inference procedures, and its evaluation.
\end{abstract}

@@

% Emphasis here is on documentation generation, so it makes little sense to
% compare this aspect of CamFort to ad hoc testing. Apples and oranges.
\item A specification concisely captures the access pattern of a
  stencil and turns it into documentation. The inference procedure
  efficiently produces specifications with no programmer intervention,
  automatically inserting specifications at appropriate places in the
  source code.
%
\item Specifications are integrated into the code as comments for easy
  integration with existing tools, as well as documentation systems (\eg{}, we
  support Doxygen and FORD syntax).
%
\item Our specification format is deliberately abstract, with a small number of
  combinators that \emph{do not involve any indexing expressions}, \eg{}
  \texttt{a(i+1,j-1)}. This contrasts with other specification approaches. If a
  user specifies, say, the Naiver-Stokes stencil above, in a deductive
  verification language such as ACSL, they must write a specification involving
  textually dense array-indexing expressions. Therefore, any low-level mistakes
  that could be made whilst programming complex indexing code could also be
  made when writing its specification. Our specifications are more abstract and
  lightweight with the aim of aiding adoption by scientists and preventing
  indexing errors.
\end{itemize}

It should be noted that our verification tool does not target the
class of bugs that can be detected automatically (\emph{push-button
  verification}). Instead, stencil computation bugs must be
identified relative to a specification of the intended behaviour.
